\chapter{User studies questionnaires}
\chlab{questionnaires}

In this chapter, we provide the contents of the questionnaires that the experiment participants were asked to complete. For both the \IDa\ and \IDb\ version-specific questionnaires, the same questions, as presented in \secref{questionnaire_ns}, have been used. For the general questionnaire the users were asked to fill in at the end of the experiment, the questions from \secref{questionnaire} have been asked.



\section{Version-specific questions}
\seclab{questionnaire_ns}


\subsection*{SUS \& UMUX questions}
Please rate the following statements on a scale of 1 (strongly disagree) to 5 (strongly agree).
\begin{enumerate}
\item I think that I would like to use this system frequently;
\item I thought the system was easy to use;
\item I think I could use the system without the support of a technical person;
\item I found the various functions in the system were well integrated;
\item I thought there was a lot of consistency in the system;
\item I would imagine that most people would learn to use this system very quickly;
\item I found the system very intuitive;
\item I felt very confident using the system;
\item I could use the system without having to learn anything new;
\item I think the system meets up with its requirements.
\end{enumerate}


\subsection*{Open questions}
Please take some time to write a few short assessments of the system.
\begin{enumerate}
\item From a chemist's point of view, please describe in a few sentences what was good about the system;
\item From a chemist's point of view, please describe in a few sentences what could be improved;
\item From the perspective of interaction with the system, please describe in a few sentences what was good;
\item From the perspective of interaction with the system, please describe in a few sentences what could be improved;
\item Did you encounter any problems with the system during the experiment? If so, please describe them in a few sentences;
\item Do you have any other comments about the system? If so, please provide them.
\end{enumerate}



\section{General questions}
\seclab{questionnaire}
Please answer the following questions.
\begin{enumerate}
\item Which of the two versions you tested do you prefer?
\item Please explain why you prefer that version;
\item Would you like to see some functionality of the other version being transferred to your preferred version? If so, please describe in a few sentences;
\item Would you like to see other functionality added to the system? If so, please describe in a few sentences;
\item Do you have any other comments about the system? If so, please provide them.
\end{enumerate}
